Ana Data

### 2025-08-10 RussoPaper/AnaDataAnalysis.Rmd
ana update

```{r echo = F, warning=FALSE, message=FALSE}

@@

temp = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/RussoPaper/20250621_AllAnaData.csv")

temp$Genotype[temp$Genotype == "WT-cr/LoxP"] = "WT(cr/LoxP)"
temp$Genotype[temp$Genotype == "G85R"] = "G85R(cr/hr)"
temp$Genotype[temp$Genotype == "G85Rcr/G85Rhr"] = "G85R(cr/hr)"

temp$Genotype[temp$Genotype == "OK371 > gbb [WT]"] = "OK371-gbb; WT(cr/LoxP)"
temp$Genotype[temp$Genotype == "OK371 > gbb [G85R]"] = "OK371-gbb; G85R(cr/LoxP)"
temp$Genotype[temp$Genotype == "OK371>gbb [WT]"] = "OK371-gbb; WT(cr/LoxP)"
temp$Genotype[temp$Genotype == "OK371>gbb [G85R]"] = "OK371-gbb; G85R(cr/LoxP)"
temp$Genotype[temp$Genotype == "OK371>gbb [WTcr/LoxP]"] = "OK371-gbb; WT(cr/LoxP)"
temp$Genotype[temp$Genotype == "OK371>gbb [G85cr/G85Rhr]"] = "OK371-gbb; G85R(cr/LoxP)"

temp$Genotype[temp$Genotype == "OK371 > saxA [WT]"] = "OK371-saxA; WT(cr/LoxP)"
temp$Genotype[temp$Genotype == "OK371 > saxA [G85R]"] = "OK371-saxA; G85R(cr/LoxP)"
temp$Genotype[temp$Genotype == "OK371> saxA [WT-cr/LoxP]"] = "OK371-saxA; WT(cr/LoxP)"
temp$Genotype[temp$Genotype == "OK371>saxA G85R"] = "OK371-saxA; G85R(cr/LoxP)"
temp$Genotype[temp$Genotype == "OK371>saxA [WTcr/LoxP]"] = "OK371-saxA; WT(cr/LoxP)"
temp$Genotype[temp$Genotype == "OK371>saxA [G85Rcr/G85Rhr]"] = "OK371-saxA; G85R(cr/LoxP)"

@@

Boutons = temp[temp$Data == "Boutons",]
boutdata = Boutons[Boutons$NMJ == "4" &
                        Boutons$Segment == "3",]

@@

Boutons = temp[temp$Data == "Boutons",]
boutdata = Boutons[Boutons$NMJ == "6-7" &
                        Boutons$Segment == "3",]

@@

@@

Boutons = temp[temp$Data == "Boutons",]
boutdata = Boutons[Boutons$NMJ == "4" &
                     (Boutons$Genotype == "WT(cr/LoxP)" | Boutons$Genotype == "G85R(cr/hr)"),]
boutdata$Genotype = paste(boutdata$Segment, boutdata$Genotype)

@@

@@

@@

lines(x = c(2.5,2.5),
      y = c(-2.5,50),
      lty = 2,
      xpd = T)

lines(x = c(4.5,4.5),
      y = c(-2.5,50),
      lty = 2,
      xpd = T)

lines(x = c(6.5,6.5),
      y = c(-2.5,50),
      lty = 2,
      xpd = T)

  y.at = c(0, 10*1:5)

@@

@@

@@

@@

@@

>>>>

```{r echo=F, message=FALSE, warning=FALSE}

@@

temp = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/RussoPaper/20250809_AllAnaData.csv", row.names = 1)
temp = temp[temp$Boutons != "x",]
temp$Boutons = as.numeric(temp$Boutons)
temp$Genotype[temp$Genotype == "WT-cr/LoxP"] = "WT(cr/LoxP)"
temp$Genotype[temp$Genotype == "G85R"] = "G85R(cr/hr)"
temp$Genotype[temp$Genotype == "G85Rcr/G85Rhr"] = "G85R(cr/hr)"

temp$Genotype[temp$Genotype == "OK371 > gbb [WT]"] = "OK371-gbb; WT(cr/LoxP)"
temp$Genotype[temp$Genotype == "OK371 > gbb [G85R]"] = "OK371-gbb; G85R(cr/LoxP)"
temp$Genotype[temp$Genotype == "OK371>gbb [WT]"] = "OK371-gbb; WT(cr/LoxP)"
temp$Genotype[temp$Genotype == "OK371>gbb [G85R]"] = "OK371-gbb; G85R(cr/LoxP)"
temp$Genotype[temp$Genotype == "OK371>gbb [WTcr/LoxP]"] = "OK371-gbb; WT(cr/LoxP)"
temp$Genotype[temp$Genotype == "OK371>gbb [WT-cr/LoxP]"] = "OK371-gbb; WT(cr/LoxP)"
temp$Genotype[temp$Genotype == "OK371>gbb [G85Rcr/G85Rhr]"] = "OK371-gbb; G85R(cr/LoxP)"
temp$Genotype[temp$Genotype == "OK371>gbb [G85cr/G85Rhr]"] = "OK371-gbb; G85R(cr/LoxP)"

temp$Genotype[temp$Genotype == "OK371 > saxA [WT]"] = "OK371-saxA; WT(cr/LoxP)"
temp$Genotype[temp$Genotype == "OK371 > saxA [G85R]"] = "OK371-saxA; G85R(cr/LoxP)"
temp$Genotype[temp$Genotype == "OK371> saxA [WT-cr/LoxP]"] = "OK371-saxA; WT(cr/LoxP)"
temp$Genotype[temp$Genotype == "OK371>saxA G85R"] = "OK371-saxA; G85R(cr/LoxP)"
temp$Genotype[temp$Genotype == "OK371>saxA [WTcr/LoxP]"] = "OK371-saxA; WT(cr/LoxP)"
temp$Genotype[temp$Genotype == "OK371>saxA [WT-cr/LoxP]"] = "OK371-saxA; WT(cr/LoxP)"
temp$Genotype[temp$Genotype == "OK371>saxA [G85Rcr/G85Rhr]"] = "OK371-saxA; G85R(cr/LoxP)"

@@

Boutons = temp[temp$Data == "Boutons",]
boutdata = Boutons[Boutons$NMJ == "4" &
                        Boutons$Segment == "3",]
boutdata$Boutons = as.numeric(boutdata$Boutons)

@@

Boutons = temp[temp$Data == "Boutons",]
boutdata = Boutons[Boutons$NMJ == "4" &
                        Boutons$Segment == "5",]
boutdata = boutdata[boutdata$Boutons != "x",]
boutdata$Boutons = as.numeric(boutdata$Boutons)

@@

Boutons = temp[temp$Data == "Boutons",]
boutdata = Boutons[Boutons$NMJ == "6-7" &
                        Boutons$Segment == "3",]
boutdata$Boutons = as.numeric(boutdata$Boutons)

Boutons = temp[temp$Data == "Boutons",]
boutdata = Boutons[Boutons$NMJ == "6-7" &
                        Boutons$Segment == "5",]
boutdata = boutdata[boutdata$Boutons != "x",]
boutdata$Boutons = as.numeric(boutdata$Boutons)
geno = unique(boutdata$Genotype)
labels = c("WT", "G85R",
           "OK-gbb WT", "OK-gbb G85R",
           "OK-SaxA WT", "OK-SaxA G85R")

@@

```{r echo = F, fig.width = 10}

Boutons = temp[temp$Data == "Boutons",]

#boutdata = Boutons[Boutons$NMJ == "4" &
#                     (Boutons$Genotype == "WT(cr/LoxP)" | #Boutons$Genotype == "G85R(cr/hr)"),]

boutdata = Boutons[Boutons$NMJ == "4",]
boutdata$Genotype = paste(boutdata$Segment, boutdata$Genotype)

geno = unique(boutdata$Genotype)
geno = geno[c(1,5, 9:12, 
              2,6, 
              3,7, 13:16,
              4,8)]

@@

boutmeans = c(mean(boutdata[boutdata$Genotype == geno[1], "Boutons"]),
              mean(boutdata[boutdata$Genotype == geno[2], "Boutons"]),
              mean(boutdata[boutdata$Genotype == geno[3], "Boutons"]),
              mean(boutdata[boutdata$Genotype == geno[4], "Boutons"]),
              mean(boutdata[boutdata$Genotype == geno[5], "Boutons"]),
              mean(boutdata[boutdata$Genotype == geno[6], "Boutons"]),
              mean(boutdata[boutdata$Genotype == geno[7], "Boutons"]),
              mean(boutdata[boutdata$Genotype == geno[8], "Boutons"]),
              mean(boutdata[boutdata$Genotype == geno[9], "Boutons"]),
              mean(boutdata[boutdata$Genotype == geno[10], "Boutons"]),
              mean(boutdata[boutdata$Genotype == geno[11], "Boutons"]),
              mean(boutdata[boutdata$Genotype == geno[12], "Boutons"]),
              mean(boutdata[boutdata$Genotype == geno[13], "Boutons"]),
              mean(boutdata[boutdata$Genotype == geno[14], "Boutons"]),
              mean(boutdata[boutdata$Genotype == geno[15], "Boutons"]),
              mean(boutdata[boutdata$Genotype == geno[16], "Boutons"]))

@@

lines(x = c(2.65,3.35),
     y = rep(boutmeans[3], 2),
     type = 'l',
     lwd = 3,
     col = std.colors[3])

lines(x = c(5.65,6.35),
     y = rep(boutmeans[6], 2),
     type = 'l',
     lwd = 3,
     col = std.colors[6])

@@

lines(x = c(8.65,9.35),
     y = rep(boutmeans[9], 2),
     type = 'l',
     lwd = 3,
     col = std.colors[1])

lines(x = c(9.65,10.35),
     y = rep(boutmeans[10], 2),
     type = 'l',
     lwd = 3,
     col = std.colors[2])

lines(x = c(10.65,11.35),
     y = rep(boutmeans[11], 2),
     type = 'l',
     lwd = 3,
     col = std.colors[3])

lines(x = c(11.65,12.35),
     y = rep(boutmeans[12], 2),
     type = 'l',
     lwd = 3,
     col = std.colors[4])

lines(x = c(12.65,13.35),
     y = rep(boutmeans[13], 2),
     type = 'l',
     lwd = 3,
     col = std.colors[5])

lines(x = c(13.65,14.35),
     y = rep(boutmeans[14], 2),
     type = 'l',
     lwd = 3,
     col = std.colors[6])

lines(x = c(14.65,15.35),
     y = rep(boutmeans[15], 2),
     type = 'l',
     lwd = 3,
     col = std.colors[1])

lines(x = c(15.65,16.35),
     y = rep(boutmeans[16], 2),
     type = 'l',
     lwd = 3,
     col = std.colors[2])

beeswarm(boutdata$Boutons~boutdata$Genotype,
       pch = 21,
       method = "center",
       bg = hex(std.colors[c(1:6, 1:2, 1:6, 1:2)],.5),
       add = T)

lines(x = c(6.5,6.5),
      y = c(-2.5,70),
      lty = 2,
      xpd = T)

lines(x = c(8.5,8.5),
      y = c(-2.5,70),
      lty = 2,
      xpd = T)

lines(x = c(14.5,14.5),
      y = c(-2.5,70),
      lty = 2,
      xpd = T)

axis(side = 1,
     at = c(3.5, 7.5, 11.5, 15.5),
     labels = c(3,4,5,6),
     las = 1,
     lwd = 0,
     line = -.75)

axis(side = 1,
     at = c(8.5),
     labels = c("Larval Segment"),
     las = 1,
     lwd = 0,
     cex = 2,
     line = 0.5)

    lines(x = c(-.10, length(na.omit(boutmeans))+.5),
       y = c(0,0),
       lwd = 3,
       xpd = T)

  y.at = c(0, 10*1:7)

@@

  legend('topright',
       inset=c(-0.14,0),
       legend = c('WT(cr/LoxP)', 'G85R(cr/hr)', 
                  "OK371-gbb; WT(cr/LoxP)", "OK371-gbb; G85R(cr/LoxP)",
                  "OK371-saxA; WT(cr/LoxP)","OK371-saxA; G85R(cr/LoxP)"), 
       fill = std.colors[1:6],
       cex = .5,
       bty = 'n',
       pt.cex = .4,
       xpd = T)

@@

t.data = list("3 WT(cr/LoxP)" = btd$Boutons[btd$Genotype == "3 WT(cr/LoxP)"],
              "3 G85R(cr/hr)" = btd$Boutons[btd$Genotype == "3 G85R(cr/hr)"],
              "3 OK371-gbb; WT(cr/LoxP)" = btd$Boutons[btd$Genotype == "3 OK371-gbb; WT(cr/LoxP)"],
              "3 OK371-gbb; G85R(cr/LoxP)" = btd$Boutons[btd$Genotype == "3 OK371-gbb; G85R(cr/LoxP)"],
              "3 OK371-saxA; WT(cr/LoxP)" = btd$Boutons[btd$Genotype == "3 OK371-saxA; WT(cr/LoxP)"],
              "3 OK371-saxA; G85R(cr/LoxP)" = btd$Boutons[btd$Genotype == "3 OK371-saxA; G85R(cr/LoxP)"],
              "4 WT(cr/LoxP)" = btd$Boutons[btd$Genotype == "4 WT(cr/LoxP)"],
              "4 G85R(cr/hr)" = btd$Boutons[btd$Genotype == "4 G85R(cr/hr)"],
              "5 WT(cr/LoxP)" = btd$Boutons[btd$Genotype == "5 WT(cr/LoxP)"],
              "5 G85R(cr/hr)" = btd$Boutons[btd$Genotype == "5 G85R(cr/hr)"],
              "5 OK371-gbb; WT(cr/LoxP)" = btd$Boutons[btd$Genotype == "5 OK371-gbb; WT(cr/LoxP)"],
              "5 OK371-gbb; G85R(cr/LoxP)" = btd$Boutons[btd$Genotype == "5 OK371-gbb; G85R(cr/LoxP)"],
              "5 OK371-saxA; WT(cr/LoxP)" = btd$Boutons[btd$Genotype == "5 OK371-saxA; WT(cr/LoxP)"],
              "5 OK371-saxA; G85R(cr/LoxP)" = btd$Boutons[btd$Genotype == "5 OK371-saxA; G85R(cr/LoxP)"],
              "6 WT(cr/LoxP)" = btd$Boutons[btd$Genotype == "6 WT(cr/LoxP)"],
              "6 G85R(cr/hr)" = btd$Boutons[btd$Genotype == "6 G85R(cr/hr)"])

@@

```{r echo = F, fig.width = 7, include = F}

@@

```{r echo = F, fig.width = 10}

Boutons = temp[temp$Data == "Boutons",]

#boutdata = Boutons[Boutons$NMJ == "6-7" &
#                     (Boutons$Genotype == "WT(cr/LoxP)" | #Boutons$Genotype == "G85R(cr/hr)"),]

boutdata = Boutons[Boutons$NMJ == "6-7",]
boutdata$Genotype = paste(boutdata$Segment, boutdata$Genotype)

geno = unique(boutdata$Genotype)
geno = geno[c(1,5, 9:12, 
              2,6, 
              3,7, 13:16,
              4,8)]

boutmeans = c(mean(boutdata[boutdata$Genotype == geno[1], "Boutons"]),
              mean(boutdata[boutdata$Genotype == geno[2], "Boutons"]),
              mean(boutdata[boutdata$Genotype == geno[3], "Boutons"]),
              mean(boutdata[boutdata$Genotype == geno[4], "Boutons"]),
              mean(boutdata[boutdata$Genotype == geno[5], "Boutons"]),
              mean(boutdata[boutdata$Genotype == geno[6], "Boutons"]),
              mean(boutdata[boutdata$Genotype == geno[7], "Boutons"]),
              mean(boutdata[boutdata$Genotype == geno[8], "Boutons"]),
              mean(boutdata[boutdata$Genotype == geno[9], "Boutons"]),
              mean(boutdata[boutdata$Genotype == geno[10], "Boutons"]),
              mean(boutdata[boutdata$Genotype == geno[11], "Boutons"]),
              mean(boutdata[boutdata$Genotype == geno[12], "Boutons"]),
              mean(boutdata[boutdata$Genotype == geno[13], "Boutons"]),
              mean(boutdata[boutdata$Genotype == geno[14], "Boutons"]),
              mean(boutdata[boutdata$Genotype == geno[15], "Boutons"]),
              mean(boutdata[boutdata$Genotype == geno[16], "Boutons"]))

lines(x = c(2.65,3.35),
     y = rep(boutmeans[3], 2),
     type = 'l',
     lwd = 3,
     col = std.colors[3])

lines(x = c(5.65,6.35),
     y = rep(boutmeans[6], 2),
     type = 'l',
     lwd = 3,
     col = std.colors[6])

lines(x = c(8.65,9.35),
     y = rep(boutmeans[9], 2),
     type = 'l',
     lwd = 3,
     col = std.colors[1])

lines(x = c(9.65,10.35),
     y = rep(boutmeans[10], 2),
     type = 'l',
     lwd = 3,
     col = std.colors[2])

lines(x = c(10.65,11.35),
     y = rep(boutmeans[11], 2),
     type = 'l',
     lwd = 3,
     col = std.colors[3])

lines(x = c(11.65,12.35),
     y = rep(boutmeans[12], 2),
     type = 'l',
     lwd = 3,
     col = std.colors[4])

lines(x = c(12.65,13.35),
     y = rep(boutmeans[13], 2),
     type = 'l',
     lwd = 3,
     col = std.colors[5])

lines(x = c(13.65,14.35),
     y = rep(boutmeans[14], 2),
     type = 'l',
     lwd = 3,
     col = std.colors[6])

lines(x = c(14.65,15.35),
     y = rep(boutmeans[15], 2),
     type = 'l',
     lwd = 3,
     col = std.colors[1])

lines(x = c(15.65,16.35),
     y = rep(boutmeans[16], 2),
     type = 'l',
     lwd = 3,
     col = std.colors[2])

beeswarm(boutdata$Boutons~boutdata$Genotype,
       pch = 21,
       method = "center",
       bg = hex(std.colors[c(1:6, 1:2, 1:6, 1:2)],.5),
       add = T)

lines(x = c(6.5,6.5),
      y = c(-2.5,70),
      lty = 2,
      xpd = T)

lines(x = c(8.5,8.5),
      y = c(-2.5,70),
      lty = 2,
      xpd = T)

lines(x = c(14.5,14.5),
      y = c(-2.5,70),
      lty = 2,
      xpd = T)

axis(side = 1,
     at = c(3.5, 7.5, 11.5, 15.5),
     labels = c(3,4,5,6),
     las = 1,
     lwd = 0,
     line = -.75)

axis(side = 1,
     at = c(8.5),
     labels = c("Larval Segment"),
     las = 1,
     lwd = 0,
     cex = 2,
     line = 0.5)

    lines(x = c(-.10, length(na.omit(boutmeans))+.5),
       y = c(0,0),
       lwd = 3,
       xpd = T)

  y.at = c(0, 10*1:7)

  legend('topright',
       inset=c(-0.14,0),
       legend = c('WT(cr/LoxP)', 'G85R(cr/hr)', 
                  "OK371-gbb; WT(cr/LoxP)", "OK371-gbb; G85R(cr/LoxP)",
                  "OK371-saxA; WT(cr/LoxP)","OK371-saxA; G85R(cr/LoxP)"), 
       fill = std.colors[1:6],
       cex = .5,
       bty = 'n',
       pt.cex = .4,
       xpd = T)

t.data = list("3 WT(cr/LoxP)" = btd$Boutons[btd$Genotype == "3 WT(cr/LoxP)"],
              "3 G85R(cr/hr)" = btd$Boutons[btd$Genotype == "3 G85R(cr/hr)"],
              "3 OK371-gbb; WT(cr/LoxP)" = btd$Boutons[btd$Genotype == "3 OK371-gbb; WT(cr/LoxP)"],
              "3 OK371-gbb; G85R(cr/LoxP)" = btd$Boutons[btd$Genotype == "3 OK371-gbb; G85R(cr/LoxP)"],
              "3 OK371-saxA; WT(cr/LoxP)" = btd$Boutons[btd$Genotype == "3 OK371-saxA; WT(cr/LoxP)"],
              "3 OK371-saxA; G85R(cr/LoxP)" = btd$Boutons[btd$Genotype == "3 OK371-saxA; G85R(cr/LoxP)"],
              "4 WT(cr/LoxP)" = btd$Boutons[btd$Genotype == "4 WT(cr/LoxP)"],
              "4 G85R(cr/hr)" = btd$Boutons[btd$Genotype == "4 G85R(cr/hr)"],
              "5 WT(cr/LoxP)" = btd$Boutons[btd$Genotype == "5 WT(cr/LoxP)"],
              "5 G85R(cr/hr)" = btd$Boutons[btd$Genotype == "5 G85R(cr/hr)"],
              "5 OK371-gbb; WT(cr/LoxP)" = btd$Boutons[btd$Genotype == "5 OK371-gbb; WT(cr/LoxP)"],
              "5 OK371-gbb; G85R(cr/LoxP)" = btd$Boutons[btd$Genotype == "5 OK371-gbb; G85R(cr/LoxP)"],
              "5 OK371-saxA; WT(cr/LoxP)" = btd$Boutons[btd$Genotype == "5 OK371-saxA; WT(cr/LoxP)"],
              "5 OK371-saxA; G85R(cr/LoxP)" = btd$Boutons[btd$Genotype == "5 OK371-saxA; G85R(cr/LoxP)"],
              "6 WT(cr/LoxP)" = btd$Boutons[btd$Genotype == "6 WT(cr/LoxP)"],
              "6 G85R(cr/hr)" = btd$Boutons[btd$Genotype == "6 G85R(cr/hr)"])

@@

```{r echo = F, include=F}
library(corrplot)
cor.table = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/RussoPaper/20250701_AllAnaData_CorrelationTable.csv",header = F)
row.names(cor.table) = paste0(cor.table[,1], ".", cor.table[,2], ".", cor.table[,3])
colnames(cor.table) = paste0(cor.table[1,], ".", cor.table[2,], ".", cor.table[3,], ".", cor.table[4,])

cor.table= cor.table[,-grep("Raw", colnames(cor.table))]

cor.table[1,grep("Norm", colnames(cor.table))] = substr(cor.table[1,grep("Norm", colnames(cor.table))], 8, nchar(cor.table[1,grep("Norm", colnames(cor.table))]))

cor.matrix = cor.table[5:nrow(cor.table), 4:ncol(cor.table)]
cor.matrix = cor.matrix[grep("WT", row.names(cor.matrix)), ]

i = 1
while(i<=ncol(cor.matrix)){
  cor.matrix[,i] = as.numeric(cor.matrix[,i])
  i = i + 1
}

cor.data = as.matrix(cor.matrix)
cor.data[,1:ncol(cor.data)] = 0
cor.data = cor.data[1:ncol(cor.data),]
row.names(cor.data) = colnames(cor.data)

cor.data = data.frame(Factor1 = character(),
                      Factor2 = character(),
                      Corr = numeric())
i=1
while(i<=ncol(cor.matrix)){
  j=1
  while(j<=ncol(cor.matrix)){
    temp = na.omit(cor.matrix[,c(i,j)])
    #cor.data[j,i] = cor(temp[,1], temp[,2])
    temp.cor.data = data.frame(Factor1 = colnames(cor.matrix)[i],
                               Factor2 = colnames(cor.matrix)[j],
                               Corr = cor(temp[,1], temp[,2]))
    cor.data = rbind(cor.data, temp.cor.data)
    j=j+1
  }
  i=i+1
}

cor.data[cor.data$Factor1 == cor.data$Factor2, "Corr"] = NA

cor.data$Factor1 = factor(cor.data$Factor1, levels = unique(cor.data$Factor1))
cor.data$Factor2 = factor(cor.data$Factor2, levels = unique(cor.data$Factor2))

WT.cor.data = cor.data

cor.matrix = cor.table[5:nrow(cor.table), 4:ncol(cor.table)]
cor.matrix = cor.matrix[grep("G85R", row.names(cor.matrix)), ]

i = 1
while(i<=ncol(cor.matrix)){
  cor.matrix[,i] = as.numeric(cor.matrix[,i])
  i = i + 1
}

cor.data = as.matrix(cor.matrix)
cor.data[,1:ncol(cor.data)] = 0
cor.data = cor.data[1:ncol(cor.data),]
row.names(cor.data) = colnames(cor.data)

cor.data = data.frame(Factor1 = character(),
                      Factor2 = character(),
                      Corr = numeric())
i=1
while(i<=ncol(cor.matrix)){
  j=1
  while(j<=ncol(cor.matrix)){
    temp = na.omit(cor.matrix[,c(i,j)])
    #cor.data[j,i] = cor(temp[,1], temp[,2])
    temp.cor.data = data.frame(Factor1 = colnames(cor.matrix)[i],
                               Factor2 = colnames(cor.matrix)[j],
                               Corr = cor(temp[,1], temp[,2]))
    cor.data = rbind(cor.data, temp.cor.data)
    j=j+1
  }
  i=i+1
}

cor.data[cor.data$Factor1 == cor.data$Factor2, "Corr"] = NA

cor.data$Factor1 = factor(cor.data$Factor1, levels = unique(cor.data$Factor1))
cor.data$Factor2 = factor(cor.data$Factor2, levels = unique(cor.data$Factor2))

GR.cor.data = cor.data

WT.cor.data = WT.cor.data[as.numeric(WT.cor.data$Factor1) < as.numeric(WT.cor.data$Factor2),]
WT.cor.data$Geno = "WT"
GR.cor.data = GR.cor.data[as.numeric(GR.cor.data$Factor1) > as.numeric(GR.cor.data$Factor2),]
GR.cor.data$Geno = "G85R"

cor.data = rbind(WT.cor.data, GR.cor.data)

```{r echo = F, fig.height=8, fig.width=8, include=F}
bg.colors = colorRampPalette(c("royalblue", "deepskyblue", "yellow", "deeppink", "violetred"))(200)

plot.bg = bg.colors[100*(cor.data$Corr + 1)]

#plot.bg[cor.data$Corr == 2] = "white"

plot.cex = 2*abs(cor.data$Corr)+.5

#plot.cex[cor.data$Corr == 2] = 2.5

par(mar = c(6,6,4,3))

plot(x = as.numeric(cor.data$Factor1),
     y = as.numeric(cor.data$Factor2),
     pch = 21,
     bg = plot.bg,
     cex = plot.cex,
     xaxt = "n",
     yaxt = "n",
     ylab = "",
     xlab = "",
     bty = "n",
     main = "")

lines(x = c(.5,23),
      y = c(.5,23),
      lty = 2,
      lwd = 2)

lines(x = c(.5, .5),
      y = c(.5,21.5),
      lty = 1,
      lwd = 1,
      xpd = T)

lines(x = c(-0.25, -0.25),
      y = c(-.25,21.5),
      lty = 2,
      lwd = .5,
      xpd = T)

lines(x = c(-1.25, -1.25),
      y = c(-1.25,21.5),
      lty = 2,
      lwd = .5,
      xpd = T)

lines(x = c(-2, -2),
      y = c(-2,21.5),
      lty = 2,
      lwd = .5,
      xpd = T)

lines(x = c(.5,21.5),
      y = c(.5, .5),
      lty = 1,
      lwd = 1,
      xpd = T)

lines(y = c(-.25, -.25),
      x = c(-.25,21.5),
      lty = 2,
      lwd = .5,
      xpd = T)

text(x = 22,
     y = 0,
     labels = "Segment",
     xpd = T,
     cex = .5)

text(x = 22,
     y = -.75,
     labels = "NMJ",
     xpd = T,
     cex = .5)

text(x = 22,
     y = -1.6,
     labels = "Side",
     xpd = T,
     cex = .5)

lines(y = c(-1.25, -1.25),
      x = c(-1.25,21.5),
      lty = 2,
      lwd = .5,
      xpd = T)

lines(y = c(-2, -2),
      x = c(-2,21.5),
      lty = 2,
      lwd = .5,
      xpd = T)

axis(side = 1,
     at = c(8.5, 17, 19.5),
     lwd = 0,
     line = 2,
     labels = c("Boutons", "VNC", "NMJ"),
     xpd = T,
     las = 1,
     cex.axis = .75)

axis(side = 1,
     at = c(17, 19.5),
     lwd = 0,
     line = 3,
     labels = c("pMad", "pMad"),
     xpd = T,
     las = 1,
     cex.axis = .75)

axis(side = 1,
     at = c(1:21),
     lwd = 0,
     line = 1,
     labels = cor.table[2, 4:ncol(cor.table)],
     xpd = T,
     las = 1,
     cex.axis = .5)

axis(side = 1,
     at = c(1:21),
     lwd = 0,
     line = -.25,
     labels = cor.table[3, 4:ncol(cor.table)],
     xpd = T,
     las = 1,
     cex.axis = .5)

axis(side = 1,
     at = c(1:21),
     lwd = 0,
     line = -1.5,
     labels = cor.table[4, 4:ncol(cor.table)],
     xpd = T,
     las = 1,
     cex.axis = .5)

axis(side = 2,
     at = c(8.5, 17, 19.5),
     lwd = 0,
     line = 3,
     labels = c("Boutons", "VNC", "NMJ"),
     xpd = T,
     srt = 270,
     cex.axis = .75)

axis(side = 2,
     at = c(17, 19.5),
     lwd = 0,
     line = 2.5,
     labels = c("pMad", "pMad"),
     xpd = T,
     srt = 270,
     cex.axis = .75)

axis(side = 2,
     at = c(1:21),
     lwd = 0,
     line = 1.5,
     labels = cor.table[2, 4:ncol(cor.table)],
     xpd = T,
     las = 1,
     cex.axis = .5)

axis(side = 2,
     at = c(1:21),
     lwd = 0,
     line = 0.25,
     labels = cor.table[3, 4:ncol(cor.table)],
     xpd = T,
     las = 1,
     cex.axis = .5)

axis(side = 2,
     at = c(1:21),
     lwd = 0,
     line = -1,
     labels = cor.table[4, 4:ncol(cor.table)],
     xpd = T,
     las = 1,
     cex.axis = .5)

arrows(x0 = 22,
       y0 = 21,
       x1 = 22,
       y1 = 13,
       lwd = 2,
       xpd = T,
       length = .1)

arrows(x0 = 21,
       y0 = 22,
       x1 = 13,
       y1 = 22,
       lwd = 2,
       xpd = T,
       length = .1)

text(x = 17,
     y = 22.5,
     labels = ("Silent"),
     xpd = T)

text(x = 22.5,
     y = 17,
     labels = ("G85R"),
     srt = 270,
     xpd = T)

axis(side = 3,
     label = "Correlation for WT and G85R, All Lines",
     at = 11,
     line = 1.5,
     cex = 1.5,
     lwd = 0)

```{r echo = F, include=F}

cor.table = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/RussoPaper/20250701_AllAnaData_CorrelationTable.csv",header = F)

cor.table= cor.table[,-grep("Raw", cor.table[1,])]

cor.table[1,grep("Norm", cor.table[1,])] = substr(cor.table[1,grep("Norm", cor.table[1,])], 8, nchar(cor.table[1,grep("Norm", cor.table[1,])]))

cor.tablea = cor.table[,cor.table[2,] == "a"]
cor.tablea = cbind(cor.tablea, cor.table[,20])
cor.tablea = cbind(cor.tablea, cor.table[,1])

cor.tableb = cor.table[,cor.table[2,] == "b"]
cor.tableb = cbind(cor.tableb, cor.table[,20])
cor.tableb = cbind(cor.tableb, cor.table[,1])

colnames(cor.tablea) = paste0(cor.tablea[1,], ".", cor.tablea[3,], ".", cor.tablea[4,])
colnames(cor.tableb) = paste0(cor.tableb[1,], ".", cor.tableb[3,], ".", cor.tableb[4,])

cor.table = rbind(cor.tablea[c(1,3:nrow(cor.tablea)),],cor.tableb[5:nrow(cor.tableb),])

cor.matrix = cor.table[grep("WT", cor.table[,ncol(cor.table)]), 1:(ncol(cor.table)-1)]

i = 1
while(i<=ncol(cor.matrix)){
  cor.matrix[,i] = as.numeric(cor.matrix[,i])
  i = i + 1
}

cor.data = as.matrix(cor.matrix)
cor.data[,1:ncol(cor.data)] = 0
cor.data = cor.data[1:ncol(cor.data),]
row.names(cor.data) = colnames(cor.data)

cor.data = data.frame(Factor1 = character(),
                      Factor2 = character(),
                      Corr = numeric())
i=1
while(i<=ncol(cor.matrix)){
  j=1
  while(j<=ncol(cor.matrix)){
    temp = na.omit(cor.matrix[,c(i,j)])
    #cor.data[j,i] = cor(temp[,1], temp[,2])
    temp.cor.data = data.frame(Factor1 = colnames(cor.matrix)[i],
                               Factor2 = colnames(cor.matrix)[j],
                               Corr = cor(temp[,1], temp[,2]))
    cor.data = rbind(cor.data, temp.cor.data)
    j=j+1
  }
  i=i+1
}

cor.data[cor.data$Factor1 == cor.data$Factor2, "Corr"] = NA

cor.data$Factor1 = factor(cor.data$Factor1, levels = unique(cor.data$Factor1))
cor.data$Factor2 = factor(cor.data$Factor2, levels = unique(cor.data$Factor2))

WT.cor.data = cor.data

cor.matrix = cor.table[grep("G85R", cor.table[,ncol(cor.table)]), 1:(ncol(cor.table)-1)]

i = 1
while(i<=ncol(cor.matrix)){
  cor.matrix[,i] = as.numeric(cor.matrix[,i])
  i = i + 1
}

cor.data = as.matrix(cor.matrix)
cor.data[,1:ncol(cor.data)] = 0
cor.data = cor.data[1:ncol(cor.data),]
row.names(cor.data) = colnames(cor.data)

cor.data = data.frame(Factor1 = character(),
                      Factor2 = character(),
                      Corr = numeric())
i=1
while(i<=ncol(cor.matrix)){
  j=1
  while(j<=ncol(cor.matrix)){
    temp = na.omit(cor.matrix[,c(i,j)])
    #cor.data[j,i] = cor(temp[,1], temp[,2])
    temp.cor.data = data.frame(Factor1 = colnames(cor.matrix)[i],
                               Factor2 = colnames(cor.matrix)[j],
                               Corr = cor(temp[,1], temp[,2]))
    cor.data = rbind(cor.data, temp.cor.data)
    j=j+1
  }
  i=i+1
}

cor.data[cor.data$Factor1 == cor.data$Factor2, "Corr"] = NA

cor.data$Factor1 = factor(cor.data$Factor1, levels = unique(cor.data$Factor1))
cor.data$Factor2 = factor(cor.data$Factor2, levels = unique(cor.data$Factor2))

GR.cor.data = cor.data

WT.cor.data = WT.cor.data[as.numeric(WT.cor.data$Factor1) < as.numeric(WT.cor.data$Factor2),]
WT.cor.data$Geno = "WT"
GR.cor.data = GR.cor.data[as.numeric(GR.cor.data$Factor1) > as.numeric(GR.cor.data$Factor2),]
GR.cor.data$Geno = "G85R"

cor.data = rbind(WT.cor.data, GR.cor.data)

```{r echo = F, fig.height=8, fig.width=8, include=F}
bg.colors = colorRampPalette(c("royalblue", "deepskyblue", "yellow", "deeppink", "violetred"))(200)

plot.bg = bg.colors[100*(cor.data$Corr + 1)]

#plot.bg[cor.data$Corr == 2] = "white"

plot.cex = 2*abs(cor.data$Corr)+.5

#plot.cex[cor.data$Corr == 2] = 2.5

par(mar = c(8,8,4,3))

plot(x = as.numeric(cor.data$Factor1),
     y = as.numeric(cor.data$Factor2),
     pch = 21,
     bg = plot.bg,
     cex = plot.cex,
     xaxt = "n",
     yaxt = "n",
     ylab = "",
     xlab = "",
     bty = "n",
     main = "")

lines(x = c(.5,14),
      y = c(.5,14),
      lty = 2,
      lwd = 2)

lines(x = c(.5, .5),
      y = c(.5,11.5),
      lty = 1,
      lwd = 1,
      xpd = T)
